\cvsection{Experience}

\begin{cventries}

    \cventry
    {Academic Assistant}
    {Wrocław University of Science and Technology}
    {Wrocław}
    {Sep. 2018 - present}
    {
    \begin{cvitems}
        \item {Quarter time.}
        \item {Giving classes about system theory and classification.}
    \end{cvitems}
    }

    \cventry
    {Software Engineer}
    {Iteratec}
    {Wrocław}
    {Sep. 2018 - present}
    {
    \begin{cvitems}
        \item {Developing features using SpringBoot and Angular.}
        \item {Using german on daily basis to communicate with team and client.}
    \end{cvitems}
    }

    \cventry
    {Software Engineer / Data Scientist}
    {Wrocław University of Science and Technology}
    {Wrocław}
    {Apr. 2018 - present}
    {
    \begin{cvitems}
        \item {Conducted research under NCN grant.}
        \item {Designed and implemented machine learning framework for classifier integration using scikit-learn and spark.}
        \item {Improved classification through new methods of classifier integration.}
    \end{cvitems}
    }

    \cventry
    {Junior Software Engineer}
    {Capgemini Software Solutions Center}
    {Wrocław}
    {Apr. 2017 - Aug. 2018}
    {
    \begin{cvitems}
        \item {Implemented new features in JEE.}
        \item {Deployed and configured devops environment (SonarQube, Jenkins, Cobertura, Jacoco).}
        \item {Wrote scripts for databases in PL/SQL.}
        \item {Used german on daily basis to communicate with team.}
        \item {Member of software craftsmanship community.}
    \end{cvitems}
    }

\end{cventries}
